Adaptive Video Streaming with Optimized Bitstream Extraction and PID-based Quality Control

### 2015-11-29 tmm.tex
Add a table and change Fig.9

The performance comparisons for City, Foreman, Harbour, and Soccer are shown in Fig. \ref{fig:performance}. It can be seen that the R-D curves of the proposed method are always on the top. For each sequence, the maximum and average PSNR gain through all 10 bitrate points are calculated and listed in Table \ref{tab:results}, which shows that our extraction method can achieve a significant performance gain compared with JSVM.

@@

\begin{figure*}[t]
\centering
\subfloat[City]{
\includegraphics[width=0.5\textwidth]{City.jpg}
\label{fig:City}}
\subfloat[Foreman]{
\includegraphics[width=0.5\textwidth]{Foreman.jpg}
\label{fig:Foreman}}
\qquad
\subfloat[Harbour]{
\includegraphics[width=0.5\textwidth]{Harbour.jpg}
\label{fig:Harbour}}
\subfloat[Soccer]{
\includegraphics[width=0.5\textwidth]{Soccer.jpg}
\label{fig:Soccer}}
\caption{Performance of three bitstream extraction methods for various CIF sequences}
\label{fig:performance}
\end{figure*}

\begin{table*}[t]
\centering
\caption{Algorithm performance: Luma PSNR gain compared with JSVM}
\label{tab:results}
\begin{minipage}{0.95\linewidth}
% \renewcommand{\thefootnote}{\thempfootnote}
\centering
\begin{tabular}{c|c|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}| 
p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}}
%% |l|l| to left justify each column entry
%% |c|c| to center each column entry
%% use of \rule[]{}{} below opens up each row
\hline \hline
\multicolumn{2}{c|}{Sequence} &
{\em Bus} & {\em City} & {\em Crew} & {\em Football} & {\em Foreman} & {\em Harbour} & {\em Mobile} & {\em Soccer} \\ \hline 
\multirow{2}{*}{JSVM QL\footnote{\label{footnote:JSVM_QL} Comparing the proposed algorithm with JSVM QL} (dB)}
& Max\footnote{\label{footnote:max} Maximum PSNR gain through all bitrate constraints} & 0.37 & 0.50 & 0.13 & 0.22 & 0.23 & 0.19 & 0.25 & 0.44 \\ \cline{2-10}
& Ave\footnote{\label{footnote:ave} Average PSNR gain through all bitrate constraints} & 0.11 & 0.11 & 0.05 & 0.12 & 0.05 & 0.05 & 0.06 & 0.13 \\ \hline
\multirow{2}{*}{JSVM no QL (dB)}
& Max & 0.50 & 0.83 & 0.32 & 0.29 & 0.50 & 0.34 & 0.61 & 0.53 \\ \cline{2-10}
& Ave & 0.18 & 0.37 & 0.20 & 0.15 & 0.22 & 0.15 & 0.25 & 0.29 \\ \hline
\end{tabular}
\end{minipage}
\end{table*}

@@

\begin{figure*}[t]
\centering
\subfloat[Bandwidth fluctuates around 600kbps: PSNR average and variance in the original system are 39.63 and 0.24, while in the proposed system are 39.69 (increased by 0.06) and 0.16 (reduced by 0.08).]{
\includegraphics[width=0.47\textwidth]{Fluctuation-PSNR1.png}
\label{fig:Fluctuation-PSNR1}}\hfill
\subfloat[Bandwidth fluctuates around 800kbps: PSNR average and variance in the original system are 40.15 and 0.48, while in the proposed system are 40.62 (increased by 0.47) and 0.28 (reduced by 0.20).]{
\includegraphics[width=0.47\textwidth]{Fluctuation-PSNR2.png}
\label{fig:Fluctuation-PSNR2}}
\qquad
\subfloat[Bandwidth fluctuates around 1000kbps: PSNR average and variance in the original system are 40.37 and 0.50, while in the proposed system are 40.74 (increased by 0.40) and 0.28 (reduced by 0.22).]{
\includegraphics[width=0.47\textwidth]{Fluctuation-PSNR3.png}
\label{fig:Fluctuation-PSNR3}}\hfill
\subfloat[Bandwidth fluctuates around 1200kbps: PSNR average and variance in the original system are 40.48 and 0.63, while in the proposed system are 41.14 (increased by 0.66) and 0.21(reduced by 0.42).]{
\includegraphics[width=0.47\textwidth]{Fluctuation-PSNR4.png}
\label{fig:Fluctuation-PSNR4}}
\caption{User-perceived PSNR change with time when bandwidth fluctuates \label{fig:fluctuation-psnr}}
\end{figure*}

>>>>

The performance comparisons for City, Foreman, Harbour, and Soccer are shown in Fig. \ref{fig:extraction-performance}. It can be seen that the R-D curves of the proposed method are always on the top. For each sequence, the maximum and average PSNR gain through all 10 bitrate points are calculated and listed in Table \ref{tab:results}, which shows that our extraction method can achieve a significant performance gain compared with JSVM.

@@

\begin{figure*}[t]
\centering
\subfloat[City]{
\includegraphics[width=0.5\textwidth]{City.jpg}
\label{fig:City}}
\subfloat[Foreman]{
\includegraphics[width=0.5\textwidth]{Foreman.jpg}
\label{fig:Foreman}}
\qquad
\subfloat[Harbour]{
\includegraphics[width=0.5\textwidth]{Harbour.jpg}
\label{fig:Harbour}}
\subfloat[Soccer]{
\includegraphics[width=0.5\textwidth]{Soccer.jpg}
\label{fig:Soccer}}
\caption{Performance of three bitstream extraction methods for various CIF sequences}
\label{fig:extraction-performance}
\end{figure*}

\begin{table*}[t]
\centering
\caption{Luma PSNR gain compared with JSVM}
\label{tab:extraction-gain}
\begin{minipage}{0.95\linewidth}
% \renewcommand{\thefootnote}{\thempfootnote}
\centering
\begin{tabular}{c|c|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}| 
p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}}
%% |l|l| to left justify each column entry
%% |c|c| to center each column entry
%% use of \rule[]{}{} below opens up each row
\hline \hline
\multicolumn{2}{c|}{Sequence} &
{\em Bus} & {\em City} & {\em Crew} & {\em Football} & {\em Foreman} & {\em Harbour} & {\em Mobile} & {\em Soccer} \\ \hline 
\multirow{2}{*}{JSVM QL\footnote{\label{footnote:JSVM_QL} Comparing the proposed algorithm with JSVM QL} (dB)}
& Max\footnote{\label{footnote:max} Maximum PSNR gain through all bitrate constraints}
& 0.37 & 0.50 & 0.13 & 0.22 & 0.23 & 0.19 & 0.25 & 0.44 \\ \cline{2-10}
& Ave\footnote{\label{footnote:ave} Average PSNR gain through all bitrate constraints}
& 0.11 & 0.11 & 0.05 & 0.12 & 0.05 & 0.05 & 0.06 & 0.13 \\ \hline
\multirow{2}{*}{JSVM no QL (dB)}
& Max & 0.50 & 0.83 & 0.32 & 0.29 & 0.50 & 0.34 & 0.61 & 0.53 \\ \cline{2-10}
& Ave & 0.18 & 0.37 & 0.20 & 0.15 & 0.22 & 0.15 & 0.25 & 0.29 \\ \hline
\end{tabular}
\end{minipage}
\end{table*}

\begin{table*}[t]
\centering
\caption{Luma PSNR gain compared with JSVM QL for different windows sizes}
\label{tab:extraction-gain-more}
\begin{minipage}{0.95\linewidth}
% \renewcommand{\thefootnote}{\thempfootnote}
\centering
\begin{tabular}{c|c|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}| 
p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}|p{1.2cm}<{\centering}}
%% |l|l| to left justify each column entry
%% |c|c| to center each column entry
%% use of \rule[]{}{} below opens up each row
\hline \hline
\multicolumn{2}{c|}{Sequence} &
{\em Bus} & {\em City} & {\em Crew} & {\em Football} & {\em Foreman} & {\em Harbour} & {\em Mobile} & {\em Soccer} \\ \hline 
\multirow{2}{*}{PSNR gain}
& 32 frames & 0.11 & 0.11 & 0.05 & 0.12 & 0.05 & 0.05 & 0.06 & 0.13 \\ \cline{2-10}
& 48 frames & 0.12 & 0.23 & 0.16 & 0.13 & 0.15 & 0.13 & 0.08 & 0.21 \\ \hline

\end{tabular}
\end{minipage}
\end{table*}

@@

\begin{figure*}[t]
\centering
\subfloat[Bandwidth fluctuates around 400kbps: PSNR average and variance in the original system are 36.00 and 0.30, while in the proposed system are 36.50 (increased by 0.50) and 0.23 (reduced by 0.07).]{
\includegraphics[width=0.47\textwidth]{Fluctuation-PSNR1.png}
\label{fig:Fluctuation-PSNR1}}\hfill
\subfloat[Bandwidth fluctuates around 600kbps: PSNR average and variance in the original system are 37.06 and 0.61, while in the proposed system are 37.32 (increased by 0.26) and 0.33 (reduced by 0.28).]{
\includegraphics[width=0.47\textwidth]{Fluctuation-PSNR2.png}
\label{fig:Fluctuation-PSNR2}}
\qquad
\subfloat[Bandwidth fluctuates around 800kbps: PSNR average and variance in the original system are 37.92 and 1.24, while in the proposed system are 38.75 (increased by 0.83) and 0.69 (reduced by 0.55).]{
\includegraphics[width=0.47\textwidth]{Fluctuation-PSNR3.png}
\label{fig:Fluctuation-PSNR3}}\hfill
\subfloat[Bandwidth fluctuates around 1000kbps: PSNR average and variance in the original system are 38.28 and 1.30, while in the proposed system are 38.94 (increased by 0.66) and 0.71 (reduced by 0.59).]{
\includegraphics[width=0.47\textwidth]{Fluctuation-PSNR4.png}
\label{fig:Fluctuation-PSNR4}}
\caption{User-perceived PSNR change with time when bandwidth fluctuates \label{fig:fluctuation-psnr}}
\end{figure*}
